Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2021-07-15 jss/EpiCompare-paper/EpiCompare-paper.Rmd
minor commit for EpiComparepaper

With many visualization and exploratory tools, models and modeling paradigms, and reviews and comparisons in the literature and through the MIDAS (Models of Infectious Disease Agent Study) network \citep{midasnetwork2021} available, this field has a number of devices to \shannon{\sout{aid}} \shannon{help}\footnote{\ben{[Ben says: I'm not sure this an improvement]}}  an individual practitioner decide the correct approach. For example, \proglang{R} packages such as \pkg{surveillance}, \pkg{EpiModel}, and \pkg{pomp} have all made significant steps in standardizing the flow of the data analysis pipeline for epidemic modeling through digitizing data sets, making accessible statistical models, and providing a plethora of educational material for both coding novices and experts alike \citep{surveillance2017,Jenness2018,King2016}.

@@

\footnote{\ben{[Ben says: Generally I found this whole section to be pretty passive and not well motivated on why we'd actually do the analysis.]}}
To conclude our paper, we demonstrate the capabilities of \pkg{EpiCompare} with a complete data analysis of a measles outbreak in 1861-1862 Germany.  Specifically, we demonstrate how tools in \pkg{EpiCompare} can be used in each step of the data analysis pipeline \footnote{\ben{[Ben says: based on an earlier read of this section, I might suggest something like "and streamline the analysis process" - is that a selling point you want to highlight?]} \shannon{check out new re-write.  new goal is to motivate question of hagelloch and then show how epicompare helps}} \ben{\sout{(see Figure \ref{fig:pipeline})}}\footnote{\ben{[Ben says: It's unclear why you want to highlight the figure again - could you be clearere on that? / what does it add to the conv/ why should they reference it?]}}.  Additionally, we highlight how time-invariant analysis (see Section \ref{sec:time-invariant}) can be used to enhance understanding of an outbreak\footnote{\ben{[Ben says: I'm not sure this is necessary to state. Additionally - is it really true do we highlight this?]}}.

@@

>>>>

With many visualization and exploratory tools, models and modeling paradigms, and reviews and comparisons in the literature and through the MIDAS (Models of Infectious Disease Agent Study) network \citep{midasnetwork2021} available, this field has a number of devices to \shannon{\sout{aid}} \shannon{help}[b] an individual practitioner decide the correct approach. For example, \proglang{R} packages such as \pkg{surveillance}, \pkg{EpiModel}, and \pkg{pomp} have all made significant steps in standardizing the flow of the data analysis pipeline for epidemic modeling through digitizing data sets, making accessible statistical models, and providing a plethora of educational material for both coding novices and experts alike \citep{surveillance2017,Jenness2018,King2016}.

@@

\footnote{\ben{[Ben says: Generally I found this whole section to be pretty passive and not well motivated on why we'd actually do the analysis.]}}
To conclude our paper, we demonstrate the capabilities of \pkg{EpiCompare} with a complete data analysis of a measles outbreak in 1861-1862 Germany.  Specifically, we demonstrate how tools in \pkg{EpiCompare} can be used in each step of the data analysis pipeline [c]\shannon{check out new re-write.  new goal is to motivate question of hagelloch and then show how epicompare helps}} (see Figure \ref{fig:pipeline})[d].  Additionally, we highlight how time-invariant analysis (see Section \ref{sec:time-invariant}) can be used to enhance understanding of an outbreak\footnote{\ben{[Ben says: I'm not sure this is necessary to state. Additionally - is it really true do we highlight this?]}}.

@@

[a]Welcome to "trackdown" version of our Rmd document. Hopefully this is useful for discussions. Let's try to convert \sout{} and colors to make it cleaner.
[b]Ben says: I'm not sure this an improvement
[c]based on an earlier read of this section, I might suggest something like "and streamline the analysis process" - is that a selling point you want to highlight?
[d]Ben says: It's unclear why you want to highlight the figure again - could you be clearer on that? / what does it add to the conv/ why should they reference it?

### 2021-07-15 jss/EpiCompare-paper/EpiCompare-paper.tex
minor commit for EpiComparepaper

With many visualization and exploratory tools, models and modeling
paradigms, and reviews and comparisons in the literature and through the
MIDAS (Models of Infectious Disease Agent Study) network
\citep{midasnetwork2021} available, this field has a number of devices
to \textcolor{orange}{\sout{aid}}
\textcolor{orange}{help}\footnote{\textcolor{violet}{[Ben says: I'm not sure this an improvement]}}
an individual practitioner decide the correct approach. For example,
\proglang{R} packages such as \pkg{surveillance}, \pkg{EpiModel}, and
\pkg{pomp} have all made significant steps in standardizing the flow of
the data analysis pipeline for epidemic modeling through digitizing data
sets, making accessible statistical models, and providing a plethora of
educational material for both coding novices and experts alike
\citep{surveillance2017,Jenness2018,King2016}.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> hagelloch_sir <- hagelloch_raw %>%
+   agents_to_aggregate(states = c(tI, tR),
+                       min_max_time = c(0, 55)) %>%
+   rename(time = t, S = X0, I = X1, R = X2)
R> 
R> 
R> ggplot(hagelloch_sir, aes(x = S, y = I, z = R))+
+   coord_tern() +
+   geom_path() +
+   labs(x = "S", y = "I", z = "R",
+        title = "Time invariant view of Hagelloch measles outbreak") + 
+   theme_sir(base_size = 24)
\end{CodeInput}
\begin{figure}[H]

@@

\begin{CodeChunk}
\begin{CodeInput}
R> both_models <- bind_rows(agg_model, fortified_net)
R> 
R> 
R> g <- ggplot() + geom_prediction_band(data = both_models %>% filter(t != 0) %>%
+                   mutate(Type = factor(Type, levels = c("Simple SIR", 
+                                                         "EpiModel SIR"))),
+          aes(x = X0, y = X1, z = X2,
+               sim_group = sim, fill = Type),
+          alpha = .5,
+          conf_level = .90) 
\end{CodeInput}
\end{CodeChunk}

@@

\footnote{\textcolor{violet}{[Ben says: Generally I found this whole section to be pretty passive and not well motivated on why we'd actually do the analysis.]}}
To conclude our paper, we demonstrate the capabilities of
\pkg{EpiCompare} with a complete data analysis of a measles outbreak in
1861-1862 Germany. Specifically, we demonstrate how tools in
\pkg{EpiCompare} can be used in each step of the data analysis pipeline
\footnote{\textcolor{violet}{[Ben says: based on an earlier read of this section, I might suggest something like "and streamline the analysis process" - is that a selling point you want to highlight?]} \textcolor{orange}{check out new re-write.  new goal is to motivate question of hagelloch and then show how epicompare helps}}
\textcolor{violet}{\sout{(see Figure \ref{fig:pipeline})}}\footnote{\textcolor{violet}{[Ben says: It's unclear why you want to highlight the figure again - could you be clearere on that? / what does it add to the conv/ why should they reference it?]}}.
Additionally, we highlight how time-invariant analysis (see Section
\ref{sec:time-invariant}) can be used to enhance understanding of an
outbreak\footnote{\textcolor{violet}{[Ben says: I'm not sure this is necessary to state. Additionally - is it really true do we highlight this?]}}.

@@

>>>>

With many visualization and exploratory tools, models and modeling
paradigms, and reviews and comparisons in the literature and through the
MIDAS (Models of Infectious Disease Agent Study) network
\citep{midasnetwork2021} available, this field has a number of devices
to \textcolor{orange}{\sout{aid}} \textcolor{orange}{help}{[}b{]} an
individual practitioner decide the correct approach. For example,
\proglang{R} packages such as \pkg{surveillance}, \pkg{EpiModel}, and
\pkg{pomp} have all made significant steps in standardizing the flow of
the data analysis pipeline for epidemic modeling through digitizing data
sets, making accessible statistical models, and providing a plethora of
educational material for both coding novices and experts alike
\citep{surveillance2017,Jenness2018,King2016}.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> hagelloch_sir <- hagelloch_raw %>%
+   agents_to_aggregate(states = c(tI, tR),
+                       min_max_time = c(0, 55)) %>%
+   rename(time = t, S = X0, I = X1, R = X2)
R> 
R> ggplot(hagelloch_sir, aes(x = S, y = I, z = R))+
+   coord_tern() +
+   geom_path() +
+   labs(x = "S", y = "I", z = "R",
+        title = "Time invariant view of Hagelloch measles outbreak") + 
+   theme_sir(base_size = 24)
\end{CodeInput}
\begin{figure}[H]

@@

\begin{CodeChunk}
\begin{CodeInput}
R> both_models <- bind_rows(agg_model, fortified_net)
R> 
R> g <- ggplot() + geom_prediction_band(data = both_models %>% filter(t != 0) %>%
+                   mutate(Type = factor(Type, levels = c("Simple SIR", 
+                                                         "EpiModel SIR"))),
+          aes(x = X0, y = X1, z = X2,
+               sim_group = sim, fill = Type),
+          alpha = .5,
+          conf_level = .90) 
\end{CodeInput}
\end{CodeChunk}

@@

\footnote{\textcolor{violet}{[Ben says: Generally I found this whole section to be pretty passive and not well motivated on why we'd actually do the analysis.]}}
To conclude our paper, we demonstrate the capabilities of
\pkg{EpiCompare} with a complete data analysis of a measles outbreak in
1861-1862 Germany. Specifically, we demonstrate how tools in
\pkg{EpiCompare} can be used in each step of the data analysis pipeline
{[}c{]}\textcolor{orange}{check out new re-write.  new goal is to motivate question of hagelloch and then show how epicompare helps}\}
(see Figure \ref{fig:pipeline}){[}d{]}. Additionally, we highlight how
time-invariant analysis (see Section \ref{sec:time-invariant}) can be
used to enhance understanding of an
outbreak\footnote{\textcolor{violet}{[Ben says: I'm not sure this is necessary to state. Additionally - is it really true do we highlight this?]}}.

@@

{[}a{]}Welcome to ``trackdown'' version of our Rmd document. Hopefully
this is useful for discussions. Let's try to convert \sout{} and colors
to make it cleaner. {[}b{]}Ben says: I'm not sure this an improvement
{[}c{]}based on an earlier read of this section, I might suggest
something like ``and streamline the analysis process'' - is that a
selling point you want to highlight? {[}d{]}Ben says: It's unclear why
you want to highlight the figure again - could you be clearer on that? /
what does it add to the conv/ why should they reference it?
